Extracting Application and Menu Events from UI Tutorial Videos

### 2015-05-10 paper/main.tex
Evaluations: #5, added code to run detection on 5 videos.
Modified some results and cleaned up/organized the writeup

\documentclass[12pt]{memoir}
\usepackage[backend=bibtex,style=numeric]{biblatex}
\usepackage{simplestyle}
\usepackage{enumitem}

@@

\title{Extracting Menu Navigation and Program Configuration Events 
from User Interface Video Tutorials}
\author{Daniel Seita \& Andrew Head}

@@

\textbf{This work seeks to use video processing and object recognition techniqes as
a technique to mine the usability of an application.}  Given the proliferation
of video tutorials on using different software, this provides new opportunties
to assess what complex actions are frequently performed by a variety of users.
We describe a technique for recognizing menus, detecting that an item has
been clicked in a menu, comparing this menu item to all other instances of
that same item by template matching, and then composing temporally close
menu navigations into configuration tasks.  By working with a corpus of
around 100 tutorials related to setting up the Eclipse environment for
programming tasks, we describe the configuration tasks that are performed
the most often.  We discuss how we can improve this workflow to improve the
speed and accuracy of detection in the future.

\subsection{Motivation}

@@

\subsection{Visually Reverse Engineering UIs}

@@

\subsection{Action Recognition}

Work here by Jitendra and Georgia and beyond.

\section{Data}

@@

\section{Implementation}
Here's a figure of our pipeline.  \textbf{Andrew: Add figure of pipeline.}

\section{Results}

Here we want to touch upon:
\begin{enumerate}[noitemsep]
\item How reliably can we classify UI events?
\item How long does it take for us to process one minute of video?  What are
the practical implications of this?
\item Some images that show recognition results for a few representative
screenshots of user interfaces.
\end{enumerate}

\section{Discussion}

\subsection{Limitations}

\subsection{Future Directions}

\section{Conclusion}

@@

\section{References}
\printbibliography[heading=none]

>>>>

\documentclass[10pt]{article}
\usepackage[backend=bibtex,style=numeric]{biblatex}
%\usepackage{simplestyle}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{fullpage}

@@

\title{Extracting Application and Menu Events from UI Tutorial Videos}
\author{Daniel Seita \& Andrew Head}

@@

This work seeks to use video processing and object recognition techniques as a technique to
mine the usability of an application.  Given the proliferation of video tutorials on using
different software, this provides new opportunities to assess what complex actions are frequently
performed by a variety of users.  We describe a technique for recognizing menus, detecting that an
item has been clicked in a menu, comparing this menu item to all other instances of that same item
by template matching, and then composing temporally close menu navigations into configuration tasks.
By working with a corpus of around 100 tutorials related to setting up the Eclipse environment for
programming tasks, we describe the configuration tasks that are performed the most often.  We
discuss how we can improve this workflow to improve the speed and accuracy of detection in the
future.

Our contributions include a small but effective dataset for evaluating the effectiveness of
detectors of UI menu-opening actions.

@@

@@

\section{Video Classification}

This will be Daniel's section. I'm probably not going to include any subsections to save time.

Figure~\ref{fig:alex_net} shows our accuracy results for the two AlexNet networks we trained.

Figure~\ref{fig:per_class} shows our per-class accuracy results for the ``no noise'' AlexNet
network.

\begin{figure}
\centering
  \begin{minipage}{.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{AlexNet_Accuracy}
  \caption{AlexNet accuracy results of two networks trained on two image datasets.}
  \label{fig:alex_net}
  \end{minipage}\hfill
  \begin{minipage}{.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{PerClassPerformance}
  \caption{AlexNet per-class accuracy results for the network trained on ``no noise'' data.}
  \label{fig:per_class}
  \end{minipage}
\end{figure}

Figures~\ref{fig:filters_all} and~\ref{fig:filters_nonoise} show visualizations of the 96 filters in
the first layer of AlexNet, each of which has dimension $55\times 55$.

\begin{figure}
\centering
  \begin{minipage}{.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_All}
  \caption{Visualization of filters from the network trained on all our image data.}
  \label{fig:filters_all}
  \end{minipage}\hfill
  \begin{minipage}{.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Filters_NoNoise}
  \caption{Visualization of filters from the network trained on ``no noise'' image data.}
  \label{fig:filters_nonoise}
  \end{minipage}
\end{figure}

\section{Locating Menus in a Frame Sequence}

This will be Andrew's section.

\subsection{Data}

@@

\subsection{Implementation}
Here's a figure of our (edit: Andrew's) pipeline.  \textbf{Andrew: Add figure of pipeline.}

\subsection{Menu Location Results}

Here we (edit: Andrew) want to touch upon:
\begin{enumerate}[noitemsep]
\item How reliably can we classify UI events?
\item How long does it take for us to process one minute of video?  What are
the practical implications of this?
\item Some images that show recognition results for a few representative
screenshots of user interfaces.
\end{enumerate}

\section{Discussion and Conclusion}

TODO (combining the two because we don't have a lot of space!)

@@

\printbibliography
